Cognate Priming

### 2022-12-21 docs/index.qmd
Update report

```{r}
#| label: fig-vocabulary-l1
#| fig-cap: "L1 vocabulary. Percentage of words in L1 reported to be understood from the vocabulary checklist."
#| fig-height: 5
#| fig-width: 8
sample_size <- participants %>% 
	filter(id %in% fit_0$data$id) %>% 
	count(age_group)

@@

```{r}
#| label: fig-vocabulary-total
#| fig-cap: "Total vocabulary"
#| fig-height: 5
#| fig-width: 8
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		),
		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
							levels = c("Observed", "Imputed"))
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot(aes(lp,  vocab_size_total, colour = is_imputed, fill = is_imputed)) +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
			  position = position_nudge(x = 0.3)) +
	geom_boxplot(width = 0.15, size = 1, colour = "black",
				 fill = "white", outlier.colour = NA,
				 position = position_nudge(x = 0.3)) +
	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
	geom_text(data = sample_size_lp,
			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
			  colour = "black", show.legend = FALSE, 
			  position = position_dodge(width = 2), inherit.aes = FALSE) +
	labs(y = "Receptive vocabulary", 
		 colour = "Imputed", 
		 fill = "Imputed") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(legend.position = "top", 
		  legend.title = element_blank(),
		  panel.grid.major.x = element_blank(),
		  axis.title.x = element_blank(),
		  axis.text = element_text(size = 9))
```

@@

```{r}
#| label: fig-vocabulary-conceptual
#| fig-height: 5
#| fig-width: 8
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		),
		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
							levels = c("Observed", "Imputed"))
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot(aes(lp,  vocab_size_conceptual, colour = is_imputed, fill = is_imputed)) +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
			  position = position_nudge(x = 0.3)) +
	geom_boxplot(width = 0.15, size = 1, colour = "black",
				 fill = "white", outlier.colour = NA,
				 position = position_nudge(x = 0.3)) +
	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
	geom_text(data = sample_size_lp,
			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
			  colour = "black", show.legend = FALSE, 
			  position = position_dodge(width = 2), inherit.aes = FALSE) +
	labs(y = "Receptive vocabulary", 
		 colour = "Imputed", 
		 fill = "Imputed") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(legend.position = "top", 
		  legend.title = element_blank(),
		  panel.grid.major.x = element_blank(),
		  axis.title.x = element_blank(),
		  axis.text = element_text(size = 9))
```

@@

>>>>

```{r}
#| label: fig-vocabulary-l1
#| fig-cap: "L1 vocabulary. Percentage of words in L1 reported to be understood from the vocabulary checklist."
#| fig-height: 5
#| fig-width: 11
sample_size <- participants %>% 
	filter(id %in% fit_0$data$id) %>% 
	count(age_group)

@@

```{r}
#| label: fig-vocabulary-total
#| fig-cap: "Total vocabulary"
#| fig-height: 5
#| fig-width: 11
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		),
		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
							levels = c("Observed", "Imputed"))
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot(aes(lp,  vocab_size_total, colour = is_imputed, fill = is_imputed)) +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
			  position = position_nudge(x = 0.3)) +
	geom_boxplot(width = 0.15, size = 1, colour = "black",
				 fill = "white", outlier.colour = NA,
				 position = position_nudge(x = 0.3)) +
	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
	geom_text(data = sample_size_lp,
			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
			  colour = "black", show.legend = FALSE, 
			  position = position_dodge(width = 2), inherit.aes = FALSE) +
	labs(y = "Receptive vocabulary", 
		 colour = "Imputed", 
		 fill = "Imputed") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(legend.position = "top", 
		  legend.title = element_blank(),
		  panel.grid.major.x = element_blank(),
		  axis.title.x = element_blank(),
		  axis.text = element_text(size = 9))
```

@@

```{r}
#| label: fig-vocabulary-conceptual
#| fig-height: 5
#| fig-width: 11
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		),
		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
							levels = c("Observed", "Imputed"))
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot(aes(lp,  vocab_size_conceptual, colour = is_imputed, fill = is_imputed)) +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
			  position = position_nudge(x = 0.3)) +
	geom_boxplot(width = 0.15, size = 1, colour = "black",
				 fill = "white", outlier.colour = NA,
				 position = position_nudge(x = 0.3)) +
	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
	geom_text(data = sample_size_lp,
			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
			  colour = "black", show.legend = FALSE, 
			  position = position_dodge(width = 2), inherit.aes = FALSE) +
	labs(y = "Receptive vocabulary", 
		 colour = "Imputed", 
		 fill = "Imputed") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(legend.position = "top", 
		  legend.title = element_blank(),
		  panel.grid.major.x = element_blank(),
		  axis.title.x = element_blank(),
		  axis.text = element_text(size = 9))
```

@@

## Additional stimuli properties
